Source Summaries

### 2020-04-14 paper/sourceSummaries/summary9.tex
prepped for the future summaries
Added summary 9

\section{Summary 8}

@@

\pagebreak

>>>>

\section{Summary 9}

@@

\noindent
\subsection{Classifying RFID attacks and defenses}

\noindent
Connor Leavesley

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{mitrokotsa09}

\noindent
The authors classify existing RFID attacks and discuss possible countermeasures.

\noindent
The authors are using Classification Theory. RFID attacks are being split into subgroups based on similarities and differences.

\noindent
The authors classify attacks based on the layer where the attack takes place: physical layer, network-transport layer, application layer, strategic layer, and multilayer. They discuss the attacks and offer possible solutions to the issues.

\noindent
The authors found that most of the attacks possible against RFID were at the physical layer via passive and active interference methods such as sending KILL commands, replay attacks, or destruction of the tags. Multiplayer attacks were only cryptobased attacks. Network-Transport layer had the tag attacks that are more common, such as cloning and spoofing.

\noindent
The authors offer no indication of a future direction.

\noindent
Joshua Niemann

\noindent
Jacob Ruud

\noindent
Quintin Walters

\Urlmuskip=0mu plus 1mu\relax
\pagebreak
